---
title: 'Homework #4'
author: "Nathaniel Wigdahl & Aidan Bergstein"
date: "2/16/2022"
output: html_document
---

## HW 4
### Nathaniel Wigdahl & Aidan Bergstein

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
```
```{r import dataset}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```

### Question Set 1

1.  What is the overall number of chocolate bars rated?

```{r}
count(choco)
```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

```{r}
choco %>% ggplot(aes(x = as.factor(Review.Date))) + geom_bar()
```
### Question Set 2

For each of the questions below provide at least one graphic as a basis for your answer.

   1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
   
  ```{r}
  breaks =c(1, 1.99, 2.99, 3.99, 4.99, 5.99);
  hist(choco$Rating, breaks = breaks)
  ```
  This histogram is pretty chunky, let's make it more granular
  
  ```{r}
  hist(choco$Rating, breaks = 17)
  ```
  
  Here we can see that the ratings are almost entirely distributed between 2 and 4, with a slight left skew towards one. There are also some outliers at 5. I wonder how many?
  
  ```{r}
  count(filter(choco, Rating > 4))
  ```
  So there are only two ratings above 4, which if we look closer are both ratings of 5.
  

   2.Do ratings depend on the cocoa percentage of a chocolate bar?
   
   We'll use a scatterplot to examine the relation between Rating and Cocoa.Pct
   ```{r}
   ggplot(choco, aes(x=Rating, y=Cocoa.Pct))+geom_jitter()

   ```
   
   There seems to be no linear relationship between the cocoa percentage and the rating. In fact the two highest rated chocolates have a similar percentage as three of the lowest rated chocolates.
   
   3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:
   
```{r Top three locations}
summary(as.factor(choco$Company.Location))

```

We can see the highest producing locations are the USA, Canada, and France so we'll focus our analysis on these.

```{r}
choco_primary <- filter(choco, Company.Location == c('U.S.A.', 'Canada', 'France'))
choco_primary %>% ggplot(aes(x = Company.Location, y = Rating)) + geom_boxplot()
```

From this boxplot we can see that France has the highest median value, with half its chocolates being rating at or above 3.5. Other than that these countries produce a comparable range of chocolates. 
The only other thing of note is that France and U.S.A. have lower minimums than Canada.

### Your Question

1. Discuss a question you want to investigate.
2. Answer this question by graphs.
3. Conclusions.



### Submission
In Canvas, submit an RMarkdown file with:
1. the names of all team members that worked on the document;
2. a link to the github repo you were working in;
3. code and answers to all of the questions;
4. the question you want to investigate with its answers and conclusions;
5. one paragraph commenting on the workflow;
6. a html or pdf file of the final output.



