---
title: 'Homework #4'
author: "Nathaniel Wigdahl & Aidan Bergstein"
date: "2/16/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```
```{r import dataset}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
head(choco)
```

### Question Set 1

1.  What is the overall number of chocolate bars rated?

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports.

choco %>% ggplot(aes(x = as.factor(Review.Date))) + geom_bar()

### Question Set 2

For each of the questions below provide at least one graphic as a basis for your answer.

   1. How are ratings distributed? Draw a histogram of ratings and describe it. Don’t forget to mention outliers, if there are any.
   2.Do ratings depend on the cocoa percentage of a chocolate bar?
   3. How do ratings compare across different company locations? Focus on the three locations with the most ratings:

### Your Question

1. Discuss a question you want to investigate.
2. Answer this question by graphs.
3. Conclusions.



### Submission
In Canvas, submit an RMarkdown file with:
1. the names of all team members that worked on the document;
2. a link to the github repo you were working in;
3. code and answers to all of the questions;
4. the question you want to investigate with its answers and conclusions;
5. one paragraph commenting on the workflow;
6. a html or pdf file of the final output.



